\textsc{Second-order state-constraint Hamilton-Jacobi equations}

### 2021-01-27 Drafts and notes/Old_draft_02.tex
Added Construction

\section{Introduction}\label{sec:intro}
Paper to read \cite{Ishii2017a} and \cite{Lasry1989}.

@@

\subsection{Convergence result}
\begin{thm}[Qualitative result] Assume $\Omega$ is an open, bounded and connected with $\mathrm{C}^2$ boundary domain of $\mathbb{R}^n$. Assume that $f\in \mathrm{C}(\overline{\Omega})\cap W^{1,\infty}(\Omega)$ and $1<p<2$. Let $u^\varepsilon$ be the solution to 
\begin{equation}\label{eq:PDE}
    \begin{cases}
    \lambda u^\varepsilon(x) + |Du^\varepsilon(x)|^p - f(x) - \varepsilon \Delta u^\varepsilon(x) = 0 \qquad
    \text{in}\;\Omega, \vspace{0cm}\\
    \displaystyle  \lim_{\mathrm{dist}(x,\partial \Omega)\to 0} u^\varepsilon(x) = +\infty.
    \end{cases} \tag{PDE$_\varepsilon$}
\end{equation}
Then $u^\varepsilon \rightarrow u$ locally uniformly in $\Omega$ as $\varepsilon\rightarrow 0$ and $u$ solves
\begin{equation}\label{eq:PDE0}
    \begin{cases}
    \lambda u(x) + |Du(x)|^p - f(x) \leq 0 \qquad\text{in}\;\Omega,\\
    \lambda u(x) + |Du(x)|^p - f(x) \geq 0 \qquad\text{on}\;\overline{\Omega}.
    \end{cases}\tag{PDE$_0$}   
\end{equation}
\end{thm}

\color{blue}
\begin{proof} (\textit{Added on Jan 16, 2021 - Heuristic idea}) Assume that we can get some sort of equi-continuity of the family $\{u^\varepsilon\}_{\varepsilon>0}$ in a local way, that is, for any compact sub-domain $\Omega'\subset\subset \Omega$ there is a constant $C(\Omega')$ such that
\begin{equation}\label{eq:bound}
    \Vert u^\varepsilon\Vert_{L^\infty(\Omega')} +\Vert Du^\varepsilon\Vert_{L^\infty(\Omega')} \leq C(\Omega').
\end{equation}
This should be done using Berstein's method (fill in later, and as $u$ blows up on $\partial \Omega$, this bound \eqref{eq:bound} may not be improved). Now let us assume via some subsequence $\varepsilon_j\to 0$ we have $u^{\varepsilon_j}\rightarrow u^0$ uniformly on compact subsets of $\Omega$, the interior stability of viscosity solution should yield us that 
\begin{equation*}
    \lambda u^0(x) + |Du^0(x)|^p - f(x) = 0 \qquad\text{in}\;\Omega.
\end{equation*}
The real difficulty is describing what is the behavior of $u^0$ on the boundary. As we expect it to solves \eqref{eq:PDE0}, it should be the maximal subsolution (hence, solution) to 
\begin{equation}\label{eq:S_lambda}
    \lambda u(x) + |Du(x)|^p - f(x) = 0 \qquad\text{in}\;\Omega.
\end{equation}
Let $v^\varepsilon\in \rmC^2(\Omega)\cap \rmC(\overline{\Omega})$ be the unique solution to the Dirichlet problem
\begin{equation}\label{eq:v_eps}
\begin{cases}
    \lambda v^\varepsilon(x) + |Dv^\varepsilon(x)|^p - f(x) = \varepsilon \Delta v^\varepsilon(x) &\qquad\text{in}\;\Omega,\\
    \;\;\,\quad\quad\qquad\qquad\qquad\qquad v^\varepsilon = u &\qquad \text{on}\;\partial\Omega.
\end{cases}
\end{equation}
where $u\in \rmC(\overline{\Omega})$ is the unique solution of \eqref{eq:PDE0}. Note that $v^\varepsilon\rightarrow v^0$ solves the corresponding Dirichlet problem
\begin{equation}\label{eq:v_0}
\begin{cases}
    \lambda v^0(x) + |Dv^0(x)|^p - f(x) = 0 &\qquad\text{in}\;\Omega,\\
    \;\;\,\quad\quad\qquad\qquad\qquad\qquad v^0 = u &\qquad \text{on}\;\partial\Omega.
\end{cases}
\end{equation}
\begin{lem} $v^0\equiv u$ as the unique solution to \eqref{eq:PDE0}.
\end{lem}
\begin{proof} We observe that $u$ solves \eqref{eq:PDE0} is the unique solution to the Dirichlet problem \eqref{eq:v_0} as well, thus $v^0 \equiv u$ by comparison principle.
\end{proof}
\noindent By comparison principle, we see that
\begin{equation*}
    v^\varepsilon(x)\leq u^\varepsilon(x) \qquad\text{for}\;x\in \Omega.
\end{equation*}
Let $\varepsilon\to 0$, we deduce that
\begin{equation*}
    u(x)\leq u^0(x) \qquad\text{for}\;x\in \Omega.
\end{equation*}
\end{proof}
\color{black}

>>>>

\section{Introduction}\label{sec:intro}

Let $\Omega$ be an open, bounded and connected with $\mathrm{C}^2$ boundary domain of $\mathbb{R}^n$. Let us consider the following Hamiltonian
\begin{equation*}
    H(x,\varrho) = |\varrho|^p-f(x), \qquad (x,p)\in \overline{\Omega}\times \mathbb{R}^n
\end{equation*}
where $f\in \mathrm{C}(\overline{\Omega})\cap W^{1,\infty}(\Omega)$ and $1<p<2$. Let $u^\varepsilon$ be the solution to 
\begin{equation}\label{eq:PDE}
    \begin{cases}
    \lambda u^\varepsilon(x) + H(x,Du^\varepsilon(x)) - \varepsilon \Delta u^\varepsilon(x) = 0 \qquad
    \text{in}\;\Omega, \vspace{0cm}\\
    \displaystyle  \lim_{\mathrm{dist}(x,\partial \Omega)\to 0} u^\varepsilon(x) = +\infty.
    \end{cases} \tag{PDE$_\varepsilon$}
\end{equation}
We are interested in studying the asymptotic behavior of $\{u^\varepsilon\}_{\varepsilon>0}$ as the vanishing viscosity happens: $\varepsilon\rightarrow 0$. The viscosity formulation of the corresponding state-constraint first order is
\begin{equation}\label{eq:1st}
    \begin{cases}
     \lambda u(x) + H(x,Du(x)) \leq 0\;\qquad\text{in}\;\Omega,\\
     \lambda u(x) + H(x,Du(x)) \geq 0\;\qquad\text{on}\;\overline{\Omega}.
    \end{cases}
\end{equation}
Equation \eqref{eq:1st} admits a unique viscosity solution in the space $\rmC(\overline{\Omega})$, which is also the maximal viscosity subsolution among all viscosity subsolution $v\in\rmC(\overline{\Omega})$. However, with unbounded solutions the situation is unclear.

Paper to read \cite{Ishii2017a} and \cite{Lasry1989}.

@@

\subsection{Convergence result}
Assume $\Omega$ is an open, bounded and connected with $\mathrm{C}^2$ boundary domain of $\mathbb{R}^n$. Assume that $f\in \mathrm{C}(\overline{\Omega})\cap W^{1,\infty}(\Omega)$ and $1<p<2$.

Let $u^\varepsilon$ be the solution to \eqref{eq:PDE}, we observe that if $u^\varepsilon\rightarrow u^0$ uniformly on compact subsets of $\Omega$, we see that $u(x)\rightarrow +\infty$ as $\mathrm{dist}(x,\partial \Omega)\to 0$ as well, therefore the limiting solution is not the state-constraint solution to a limiting first order equation.

\begin{lem}\label{lem:max} Let $u\in \rmC(\overline{\Omega})$ be a viscosity subsolution of 
\begin{equation}\label{S_0}
 \lambda u(x) + H(x,Du(x)) = 0\;\qquad\text{in}\;\Omega
\end{equation}
such that, for all viscosity subsolution $v\in \rmC(\overline{\Omega})$ of \eqref{S_0} one has $v\leq u$ in $\overline{\Omega}$, then $u$ is a viscosity supersolution of \eqref{S_0} on $\overline{\Omega}$.
\end{lem}
\begin{proof} We review the proof using Perron's method (see \cite{Capuzzo-Dolcetta1990}). Let $\varphi\in \rmC(\overline{\Omega})$ and $x_0\in \overline{\Omega}$ such that $u(x_0) = \varphi(x_0)$ and $u-\varphi$ has a global strict minimum over $\overline{\Omega}$ at $x_0$ and that 
\begin{equation}\label{eq:max_a1}
    \lambda \varphi(x_0) + H(x_0,D\varphi(x_0)) < 0.
\end{equation}
Let $\varphi^\varepsilon(x) = \varphi(x) - |x-x_0|^2 + \varepsilon$ for $x\in \overline{\Omega}$. Let $\delta > 0$, we see that for $x\in \partial B(x_0,\delta)\cap \overline{\Omega}$ then
\begin{equation*}
    \varphi^\varepsilon(x) = \varphi(x) - \delta^2 +\varepsilon \leq \varphi(x) - \varepsilon
\end{equation*}
if $2\varepsilon \leq \delta^2$. We observe that
\begin{equation*}
    \begin{split}
    \varphi^\varepsilon(x) - \varphi(x_0)  &= \varphi(x)-\varphi(x_0) + \varepsilon - |x-x_0|^2 \\
    D\phi^\varepsilon(x) - D\phi(x_0) &= D\varphi(x) - D\varphi(x_0) - 2(x-x_0)
    \end{split}
\end{equation*}
for $x\in B(x,\delta)\cap \overline{\Omega}$. We deduce from \eqref{eq:max_a1}, the continuity of $H(x,p)$ near $(x_0,D\varphi(x_0))$ and the fact that $\varphi\in \rmC^1(\overline{\Omega})$ that if $\delta$ is small enough and $0<2\varepsilon < \delta^2$ then
\begin{equation}\label{eq:max_a2}
    \lambda \varphi^\varepsilon(x)+H(x,D\varphi^\varepsilon(x)) < 0 \qquad\text{for}\;x\in B(x_0,\delta)\cap \overline{\Omega}.
\end{equation}
We have found $\phi^\varepsilon\in \mathrm{C}^1(\overline{\Omega})$ such that $\varphi^\varepsilon(x_0)>u(x_0)$, $\varphi^\varepsilon<u$ on $\partial B(x_0,\delta)\cap \overline{\Omega}$ and \eqref{eq:max_a2}. Let
\begin{equation*}
    \tilde{u}(x) = \begin{cases}
    \max \big\lbrace u(x),\phi^\varepsilon(x) \big\rbrace &x\in B(x_0,\delta)\cap \overline{\Omega},\\
    u(x)&x\notin B(x_0,\delta)\cap \overline{\Omega},\\
    \end{cases}
\end{equation*}
We see that $\tilde{u}\in \rmC(\overline{\Omega})$ is a subsolution of \eqref{S_0} in $\Omega$ with $\tilde{u}(x_0) > u(x_0)$, which is a contradiction, thus $u$ is a supersolution of \eqref{S_0} on $\overline{\Omega}$.
\end{proof}

\begin{thm}[Qualitative result] Assume $\Omega$ is an open, bounded and connected with $\mathrm{C}^2$ boundary domain of $\mathbb{R}^n$. Assume that $f\in \mathrm{C}(\overline{\Omega})\cap W^{1,\infty}(\Omega)$ and $1<p<2$. Let $u^\varepsilon$ be the solution to \eqref{eq:PDE}, then $u^\varepsilon \rightarrow u^0$ locally uniformly in $\Omega$ as $\varepsilon\rightarrow 0$ and $u^0$ solves
\begin{equation}\label{eq:PDE0}
    \begin{cases}
    \lambda u(x) + |Du(x)|^p - f(x)=  0 \qquad\text{in}\;\Omega, \vspace{0cm}\\
    \displaystyle  \lim_{\mathrm{dist}(x,\partial \Omega)\to 0} u^0(x) = +\infty.
    \end{cases} \tag{PDE$_0$}
\end{equation}
\end{thm}

\color{blue}
\begin{proof} (\textit{Added on Jan 16, 2021 - Heuristic idea}) Assume that we can get some sort of equi-continuity of the family $\{u^\varepsilon\}_{\varepsilon>0}$ in a local way, that is, for any compact sub-domain $\Omega'\subset\subset \Omega$ there is a constant $C(\Omega')$ such that
\begin{equation}\label{eq:bound}
    \Vert u^\varepsilon\Vert_{L^\infty(\Omega')} +\Vert Du^\varepsilon\Vert_{L^\infty(\Omega')} \leq C(\Omega').
\end{equation}
This should be done using Berstein's method (fill in later, and as $u$ blows up on $\partial \Omega$, this bound \eqref{eq:bound} may not be improved). Now let us assume via some subsequence $\varepsilon_j\to 0$ we have $u^{\varepsilon_j}\rightarrow u^0$ uniformly on compact subsets of $\Omega$, the interior stability of viscosity solution should yield us that 
\begin{equation*}
    \lambda u^0(x) + |Du^0(x)|^p - f(x) = 0 \qquad\text{in}\;\Omega.
\end{equation*}
The real difficulty is describing what is the behavior of $u^0$ on the boundary. It is clear that
\begin{equation*}
    \displaystyle  \lim_{\mathrm{dist}(x,\partial \Omega)\to 0} u^0(x) = +\infty.
\end{equation*}

In fact, for each $x_0\in \partial \Omega$, let $\Vec{\mathfrak{n}}(x_0)$ be the unit outward normal vector, consider $x_s = x_0 - s\Vec{\mathfrak{n}}(x_0)$ for $s>0$. For each $j\in \mathbb{N}$ there holds $\lim_{s\to 0} u^\varepsilon(x_s) = +\infty$, therefore we can find a subsequence $s_j \to 0$ such that 
\begin{equation*}
    u^\varepsilon(x_{s_j}) \geq \tfrac{1}{\varepsilon_j}.
\end{equation*}
\vspace{2cm}

As we expect it to solves \eqref{eq:PDE0}, it should be the maximal subsolution (hence, solution) to 
\begin{equation}\label{eq:S_lambda}
    \lambda u(x) + |Du(x)|^p - f(x) = 0 \qquad\text{in}\;\Omega.
\end{equation}
Let $v^\varepsilon\in \rmC^2(\Omega)\cap \rmC(\overline{\Omega})$ be the unique solution to the Dirichlet problem
\begin{equation}\label{eq:v_eps}
\begin{cases}
    \lambda v^\varepsilon(x) + |Dv^\varepsilon(x)|^p - f(x) = \varepsilon \Delta v^\varepsilon(x) &\qquad\text{in}\;\Omega,\\
    \;\;\,\quad\quad\qquad\qquad\qquad\qquad v^\varepsilon = u &\qquad \text{on}\;\partial\Omega.
\end{cases}
\end{equation}
where $u\in \rmC(\overline{\Omega})$ is the unique solution of \eqref{eq:PDE0}. Note that $v^\varepsilon\rightarrow v^0$ solves the corresponding Dirichlet problem
\begin{equation}\label{eq:v_0}
\begin{cases}
    \lambda v^0(x) + |Dv^0(x)|^p - f(x) = 0 &\qquad\text{in}\;\Omega,\\
    \;\;\,\quad\quad\qquad\qquad\qquad\qquad v^0 = u &\qquad \text{on}\;\partial\Omega.
\end{cases}
\end{equation}
\begin{lem} $v^0\equiv u$ as the unique solution to \eqref{eq:PDE0}.
\end{lem}
\begin{proof} We observe that $u$ solves \eqref{eq:PDE0} is the unique solution to the Dirichlet problem \eqref{eq:v_0} as well, thus $v^0 \equiv u$ by comparison principle.
\end{proof}
\noindent By comparison principle, we see that
\begin{equation*}
    v^\varepsilon(x)\leq u^\varepsilon(x) \qquad\text{for}\;x\in \Omega.
\end{equation*}
Let $\varepsilon\to 0$, we deduce that
\begin{equation*}
    u(x)\leq u^0(x) \qquad\text{for}\;x\in \Omega.
\end{equation*}
\end{proof}
\color{black}

\begin{lem} If $\delta$ is small enough then $u^0$ is a supersolution of \eqref{S_0} on $\overline{\Omega}_\delta$.
\end{lem}
\begin{proof} For $\delta>0$, let us denote $v_\delta\in\rmC(\overline{\Omega}_\delta)$ be the state-constraint viscosity subsolution to the problem $\lambda u(x) + H(x,Du(x)) = 0$ in $\Omega_\delta$, then by Lemma  \ref{lem:max} we have
\begin{equation}\label{eq:les1}
   u^0(x) \leq v_\delta(x) \qquad\text{for}\;x\in \overline{\Omega}_\delta
\end{equation}
since $u^0 \in \rmC(\overline{\Omega}_\delta)$ is a viscosity (sub)solution to $\lambda u(x) + H(x,Du(x)) = 0$ in $\Omega_\delta$. Let us denote $v^\varepsilon\in \rmC^2(\Omega_\delta)\cap \rmC(\overline{\Omega}_\delta)$ as the unique solution to the Dirichlet problem
\begin{equation}\label{eq:vv_eps}
\begin{cases}
    \lambda v^\varepsilon(x) + |Dv^\varepsilon(x)|^p - f(x) = \varepsilon \Delta v^\varepsilon(x) &\qquad\text{in}\;\Omega_\delta,\\
    \;\;\,\quad\quad\qquad\qquad\qquad\qquad v^\varepsilon = v_\delta &\qquad \text{on}\;\partial\Omega_\delta.
\end{cases}
\end{equation}
Comparing $u^\varepsilon$ and $v^\varepsilon$ on $\overline{\Omega}_\delta$, for $\delta$ small enough we have $v_\delta\leq u^\varepsilon$ on $\partial \Omega_\delta$, thus by comparison principle for \eqref{eq:vv_eps} we obtain that $v^\varepsilon \leq u^\varepsilon$ on $\overline{\Omega}_\delta$, thus as $\varepsilon\to 0$ we have
\begin{equation}\label{eq:les2}
    v_\delta(x) \leq u^0(x)  \qquad\text{for}\;x\in \overline{\Omega}_\delta.
\end{equation}
From \eqref{eq:les1} and \eqref{eq:les2} we deduce that $v_\delta = u^0$ on $\overline{\Omega}_\delta$.
\end{proof}
